Revealing Benefits, Costs, and Tradeoffs of Spatial Management Arrising from Coupled Economic and Ecological Dynamics in Marine Systems

### 2023-09-28 README.Rmd
cleaning up documentation and testing migration to speedy abalone
getting somewhere

@@

4. In the terminal, run `RUN_NAME="MyRunName" FORMAT="MyFormat" make` where MyRunName is the name of the folder you want to create to store results (e.g. v0.1) and FORMAT is one of pdf, html, or docx

>>>>

## Knitting to PDF

Note that if you want to knit to PDF you'll need to have appropriate LaTeX style software installed. I recommend [`tinytex`](https://yihui.org/tinytex/).

@@

4. In the terminal, run `RUN_NAME="MYRUNNAME" FORMAT="FORMAT" make` where MYRUNNAME is the name of the folder you want to create to store results (e.g. v0.1) and FORMAT is one of pdf, html, or docx
